A thesis draft

### 2018-10-10 draft.tex
Add something about Openbaton

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\paragraph{Openbaton}
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}

>>>>

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openvswitch}
\paragraph{Openbaton} Created by the Institute Fraunhofer, it's a open-source, 
customizable NFV MANO-compliant framework, that offers many configurations 
options, and since it's written in Java, there is the possibility to add 
components (plug-ins) dynamically. Openbaton can be installed on-permise 
installations but it can also run on Docker containers. It's designed to work 
with cloud providers like Amazon or Google Compute engine, but it offers 
compability with on-permise cloud solutions like Openstack too.
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
